### 2020-09-17 README.Rmd
Small change to SCBI section getting rid of get_model_specs
Some changes so it works for SCBI

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=factor(foldID)), size = 0.1)
```

@@

```{r, eval = run_scbi}
# SCBI
scbi_specs <- scbi_growth_df %>% 
  get_model_specs(model_number = 3, species_notion = 'sp')
scbi_specs
```

```{r, eval = run_scbi}
# SCBI
tic()
focal_vs_comp_scbi <- scbi_growth_df %>% 
  create_focal_vs_comp(max_dist, model_specs = scbi_specs, cv_grid = scbi_cv_grid, id = "stemID")
toc()
```

@@

```{r, eval = run_scbi}
# SCBI
tic()
scbi_fit_model <- focal_vs_comp_scbi %>% 
  fit_bayesian_model(model_specs = scbi_specs)
toc()
```

>>>>

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=factor(foldID)), size = 0.1)

scbi_cv_grid_sf <- scbi_cv_grid$blocks %>%
  st_as_sf()
```

@@

```{r, eval = run_scbi}
# SCBI
tic()
focal_vs_comp_scbi <- scbi_growth_df %>% 
  create_focal_vs_comp(max_dist, cv_grid_sf = scbi_cv_grid_sf, id = "stemID")
toc()
```

@@

```{r, eval = run_scbi}
# SCBI
tic()
posterior_param_scbi <- focal_vs_comp_scbi %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = TRUE)
toc()
```
